   
\documentclass[11pt]{article}
\usepackage{amsmath,amsthm,verbatim,amssymb,amsfonts,amscd, graphicx}
\usepackage{graphicx}
\usepackage{float}
\topmargin0.0cm
\headheight0.0cm
\headsep0.0cm
\oddsidemargin0.0cm
\textheight23.0cm
\textwidth16.5cm
\footskip1.0cm
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem*{surfacecor}{Corollary 1}
\newtheorem{conjecture}{Conjecture} 
\newtheorem{question}{Question} 
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\begin{document}
\title{CS 5220\\ Project 1 - Matrix Multiplication Review of Group 22}
\author{Weici Hu(wh343)\\ Sheroze Sheriffdeen(mss385)\\ Qinyu Wang(qw78)}
\maketitle

\section*{What was done well}
\begin{itemize}
	\item Clear explanation of the four optimization approaches used.
	\item Clear logic between steps. 
	\item Good performance gain from optimizations compared to provided fortran implementation.
\end{itemize}
\section*{What needs to be improved}
\begin{itemize}
	\item Could try out more compiler optimization flags. This approach has mentioned by other groups which is able to gain the most easy performance lift. 
	\item Could be more specific of what compiler and flgas are used to generate the plor.
	\item This report is more like a final show case of the project. We are also interested in seeing how do you arrived at these decisions. Namely, among all the methods you have tried, what methods did not work? Why you decided to use certain techniques.	
\end{itemize}



 
 
\end{document}